---
title: "Creating and working with corpus objects"
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "images/"
)
```

```{r}
library("quanteda")
```

## Using **magrittr**'s pipe

```{r}
data_corpus_inaugural %>% 
    corpus_subset(President == "Obama") %>% 
    ndoc()
```

### Exercise

Add a step to the above to convert the documents in the corpus into sentences.  Hint: Insert a step calling `corpus_reshape()`.

```{r}

```

## Access number of types and tokens of corpus

```{r}
ntype(data_corpus_inaugural) %>% 
    head()

ntoken(data_corpus_inaugural) %>% 
    head()
```



## Overview of document-level variables

```{r}
head(docvars(data_corpus_inaugural))
```

### Exercise

1. Based on `data_corpus_inaugural`, create an object `data_corpus_postwar` (speeches since 1945).

```{r}

```

2. What speech has most tokens? What speech has most types?

```{r}

```

Note: You can find the documentation and examples using `?` followed by the name of the function.


## Adding document-level variables

```{r}
# new docvar: PresidentFull
docvars(data_corpus_inaugural, "Order") <- 1:ndoc(data_corpus_inaugural)

head(docvars(data_corpus_inaugural, "Order"))

# new docvar: PresidentFull
docvars(data_corpus_inaugural, "PresidentFull") <- 
    paste(docvars(data_corpus_inaugural, "FirstName"),
          docvars(data_corpus_inaugural, "President"),
          sep = " ")

head(docvars(data_corpus_inaugural))
```

### Exercise

1. See `?docvars`.  Is there another way to add docvars, using an operator?  Can you reproduce the code above using that method?

```{r}

```

2. Tokenize the corpus object to which you have added docvars. Are the docvars still in the tokens object?

```{r}

```

3. Make a dfm from the corpus object.  Are the docvars still in the dfm object?

```{r}

```


