---
title: "Importing data to create corpora"
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "images/"
)
```

```{r}
# load the readtext package
library(readtext)

# data_dir is the location of sample files on your computer.
data_dir <- system.file("extdata/", package = "readtext")

eu_data <- readtext(paste0(data_dir, "/txt/EU_manifestos/*.txt"),
                    docvarsfrom = "filenames", 
                    docvarnames = c("unit", 
                                    "context", 
                                    "year", 
                                    "language",
                                    "party"),
                    dvsep = "_", 
                    encoding = "ISO-8859-1")
```


## Structure of **readtext** data frame

```{r}
head(eu_data)
```


## Check the encoding 

```{r}
file <- system.file("extdata/txt/EU_manifestos/EU_euro_2004_de_V.txt", 
                    package = "readtext")

myreadtext <- readtext(file)
encoding(myreadtext)
```



### Exercise

1. Set up a RProj in a new folder.
2. Download ZIP file with inaugural speeches by German chancellors (https://tinyurl.com/corp-regierung)
3. Copy the folder into your RProj folder.
4. Import all text files using `readtext()`. (Hint: "name_of_folder/*" reads in all files)
5. Create a text corpus of this data frame. 


## Working with the new corpus (optional)

Now we will tidy up the document variables, and then search for some terms and plot them as an "x-ray" plot.

### Exercise

1. Create better `docnames` by pasting "Year" and "Chancellor" together.
2. Select speeches by Gerhard Schröder and Angela Merkel.
3. Use `kwic()` to select the terms "Arbeits*", "Arbeitslos*" and "Migration*"
4. Send the results of the `kwic()` call to `?textplot_xray()`.

