---
title: "Creating and working with dfm objects"
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "images/"
)
```

```{r}
library("quanteda")

corp_immig <- corpus(data_char_ukimmig2010)
toks_immig <- tokens(corp_immig)
```



### Exercise

1. Create a document-feature matrix from the tokens object above.
2. Get the 50 most frequent terms using `topfeatures()`.
3. Compare this to the results of calling `textstat_frequency()`.


## Selecting features based on frequencies

On term frequency:
```{r}
data(data_corpus_irishbudget2010, package = "quanteda.textmodels")
toks_ire <- tokens(data_corpus_irishbudget2010)
dfmat_ire <- dfm(toks_ire) # dfm() transforms to lower case by default

nfeat(dfmat_ire)
dfmat_ire_trim1 <- dfm_trim(dfmat_ire, 
                       min_termfreq = 5)
nfeat(dfmat_ire_trim1)
```

### Exercise

For this, you will need to examine the manual page for `dfm_trim()`.

1. Trim the dfm to include only terms with a minimum document frequency of 5.  What does this mean, exactly?
2. Trim the documents to include only features that occur in 10% of all documents.
3. Trim all but the top 20 most frequent features.


## Weighting a dfm


### Exercise

```{r}
texts <- c("apple is better than banana",
           "banana banana apple much better")
dfm(texts)
```


1. Create a dfm from the two documents above, and weight it using `dfm_weight()`. 
2. For `dfm_weight()` try out the `scheme` arguments "count", "boolean" and "prop". 
3. What are advantages and problems of each weighting scheme?
4. Weight the dfm using td-idf weighting.


