---
title: "Classifying documents"
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "images/"
)
```

```{r}
library("quanteda")
library("quanteda.textmodels")
```

## Exercise: Movie reviews

In this exercise, we will predict the "sentiment" of movie reviews.  This makes use of `data_corpus_moviereviews` (included in **quanteda.textmodels**).  This contains 1000 positive and 1000 negative movie reviews, labelled with the document variable "sentiment".

Here is some starter code that creates a training set from 200 documents from each class.
```{r}
set.seed(100)

corp_train <- corpus_sample(data_corpus_moviereviews, size = 200,
                            by = "sentiment")

corp_test <- corpus_subset(data_corpus_moviereviews, 
                           ! docnames(data_corpus_moviereviews) %in% docnames(corp_train))


dfmat_train <- dfm(corp_train)
dfmat_test <- dfm(corp_test)

tmod <- textmodel_nb(dfmat_train, y = dfmat_train$sentiment)
```


1. Extract the predicted sentiment by fitting tmod on the dfmat_test.

```{r}

```

2. Compare this using `table()` to the actual sentiment from the human categories.  Hint: This is the `sentiment` from `dfmat_test`.

```{r}

```

3. Try to repeat the analysis using `textmodel_svm()`, and compare the results.

```{r}

```

