---
title: "Scaling documents"
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "images/"
)
```

```{r}
library("quanteda")
library("quanteda.textmodels")
```

## Exercise: Wordscores

In this exercise, we will work with the Irish budget corpus.

1. Use `data_corpus_irishbudget2010` (included in **quanteda.textmodels**) as in the slides, but set the reference documents as -1 for Richard Bruton (the opposition's shadow finance minister) and +1 for Brian Lenihan (the government finance minister).

```{r}

```

2. Examine the thetas, using `coef()`.

```{r}

```

3. Predict the values using `predict()`.

```{r}

```

4. Plot the results using `textplot_scale1d()`, and group the results by party.

```{r}

```


## Exercise: Wordfish

In this exercise, we will continue to work with the Irish budget corpus.

1. Use `data_corpus_irishbudget2010` but with `textmodel_wordfish()`.  Set the `dir` to force Bruton to be left of Lenihan.  What does this mean?

```{r}

```

2. Plot the results and compare to thw Wordscores analysis.

```{r}

```


## Exercise: Correspondence Analysis

Fit a correspondence analysis to the data using `textmodel_ca()`.  Compare the document positions from the first dimension to those from the Wordfish thetas. Do this using a scatter plot.

```{r}

```
