---
title: "Sentiment analysis"
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "images/"
)
```

```{r}
library("quanteda")
```

## Exercise

In this exercise, we work with 2000 movie reviews. This corpus is included as `data_corpus_moviereviews` in the **quanteda.textmodels** package.

```{r}
# get the text corpus
data(data_corpus_moviereviews, package = "quanteda.textmodels")
```

1. Use `data_corpus_moviereviews` (included in **quanteda.textmodels**) and apply a sentiment analysis to each review using `data_dicionary_LSD2015` as the input. Convert the `dfm` to a data frame.

```{r}

```


2. Add a new variable `log_sentiment` to the data frame: $log((positive + neg-negative + 0.5) / (negative + neg-positive + 0.5))$.

```{r}

```

3. Inspect the distribution of sentiment scores by printing summary statistics of the variable (hint: `summary(name_of_your_dataframe$log_sentiment)`).

```{r}

```

4. BONUS: Add the document-level variable "sentiment" to the data frame that contains the variables from the sentiment analysis.

```{r}

```

5. BONUS: Create a boxplot with the classified sentiment on the x-axis and the sentiment scores from the dictionary on the y-axis.

```{r}

```

