---
title: "Keywords-in-context"
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "images/"
)
```

```{r}
library("quanteda")
```


## US Inaugural Speeches

In this exercise, you will explore some of the terms and their immediate context in US inaugural speeches.

## Exercise

1. In what context were "God" and "God bless" used in US presidential inaugural speeches after 1970?

```{r}
corp_since1970 <- corpus_subset(data_corpus_inaugural, Year > 1970)

kwic(corp_since1970, pattern = "god")
```

2. Look up keywords-in-context for `god`, `god bless` (wrapping the latter in `phrase()`) in one `kwic()` call.

```{r}
kwic(corp_since1970, pattern = c("god", phrase("god bless")))

list_check <- c("god", "god bless")
kwic(corp_since1970, pattern = phrase(list_check))

my_kwic <- kwic(corp_since1970, pattern = phrase(c("god", "god bless")), window = 20)

dat_kwic <- data.frame(my_kwic)
# write.csv(dat_kwic, "dat_kwic.csv")
```

3. BONUS: Send the results of the kwic output to `textplot_xray()`.

```{r}
textplot_xray(my_kwic, scale = "relative")

textplot_xray(my_kwic, scale = "absolute")
```



