---
title: "Scaling documents"
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "images/"
)
```

```{r}
library("quanteda")
library("quanteda.textmodels")
```

## Exercise: Wordscores

In this exercise, we will work with the Irish budget corpus.

1. Use `data_corpus_irishbudget2010` (included in **quanteda.textmodels**) as in the slides, but set the reference documents as -1 for Richard Bruton (the opposition's shadow finance minister) and +1 for Brian Lenihan (the government finance minister).

```{r}
dfmat <- dfm(data_corpus_irishbudget2010)
refscores <- c(1, -1, rep(NA, 12))
tmod1 <- textmodel_wordscores(dfmat, y = refscores, smooth = 1)
```

2. Examine the thetas, using `coef()`.

```{r}
thetas_ws <- predict(tmod1)
thetas_ws
```

3. Predict the values using `predict()`.

```{r}
# same as above
```

4. Plot the results using `textplot_scale1d()`, and group the results by party.

```{r}
textplot_scale1d(predict(tmod1, se.fit = TRUE), groups = dfmat$party)
```


## Exercise: Wordfish

In this exercise, we will continue to work with the Irish budget corpus.

1. Use `data_corpus_irishbudget2010` but with `textmodel_wordfish()`.  Set the `dir` to force Bruton to be left of Lenihan.  What does this mean?

```{r}
tmod2 <- textmodel_wordfish(dfmat, dir = c(2, 1))
```

2. Plot the results and compare to the Wordscores analysis.

```{r}
words_ws <- coef(tmod1)
words_wf <- coef(tmod2, margin = "features")
length(words_ws)
head(words_ws)
length(words_wf)
head(words_wf)

df <- data.frame(words_ws, words_wf = words_wf[names(words_ws), "beta"])

library("ggplot2")
ggplot(df, aes(x = words_ws, y = words_wf)) +
    geom_point()
```

```{r}
df <- data.frame(docs_ws = predict(tmod1), 
                 docs_wf = coef(tmod2, margin = "documents")[, "theta"])
ggplot(df, aes(x = docs_ws, y = docs_wf)) +
    geom_point()
```

## Exercise: Correspondence Analysis

Fit a correspondence analysis to the data using `textmodel_ca()`.  Compare the document positions from the first dimension to those from the Wordfish thetas. Do this using a scatter plot.

```{r}
tmod_ca <- textmodel_ca(dfmat)
df <- data.frame(docs_ca = coef(tmod_ca)[["coef_document"]], 
                 docs_wf = coef(tmod2, margin = "documents")[, "theta"])
ggplot(df, aes(x = docs_ca, y = docs_wf)) +
    geom_point()
```
```{r}
textplot_scale1d(tmod_ca, groups = dfmat$party)
```

