---
title: "Wrapping up day 1 - From a data frame to a dfm"
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "images/"
)
```

```{r}
library("quanteda")
```


## Setting up an R Project

- Set up a new R Project (`File -> New Project -> New Directory -> New Project`)
- Create a subfolder called `data`.
- Download corpus of Drucksachen from the GitHub repo (stored in `data`).
- Copy and paste this file into `data`


## Exercise

1. Load the data frame into R using `dat_raw <- readRDS("data/data_corpus_drucksachen_sample.rds")`.

```{r}
# my answer
```

2. Create a text corpus from this data frame using `corpus()`.

```{r}

```

3. Based on `kwic()` explore the usage of the terms of your choice and/or "Versorgung*" and "Sozialpolitik*".

```{r}

```

4. Change the number of surrounding words to ±10.

```{r}

```

5. Create a tokens object.

```{r}

```

6. Construct a document-feature matrix (`dfm()`). and remove German stopwords, punctuation, and the term "dass".

```{r}

```

7. Get the 100 most frequent terms using `topfeatures()`.

```{r}

```

8. BONUS: Create a word cloud with the 100 most frequent terms.

```{r}

```



